Collate Rarefied Samples and Null Models

### 2022-04-27 analysis/02_rarefy_timeseries.Rmd
scrap the pins approach

Load data
```{r}
pins::board_register_github(name = "github", repo = "karinorman/biodivTS_data", branch = "master")

##	Get trait filtered data, rename colums to jive with the rest of the script
bt_traitfiltered <- pins::pin_get("bt-traitfiltered", board = "github") %>%
  rename_with(toupper) %>%
  rename(Species = SPECIES, StudyMethod = STUDYMETHOD, ObsEventID = OBSEVENTID,
         rarefyID = RAREFYID, cell = CELL, Abundance = ABUNDANCE, Biomass = BIOMASS)

trait_ref <- pins::pin_get("trait-ref", board = "github")
```

>>>>

Load data
```{r}
load(here::here("data/bt_traitfiltered.rda"))

##	Get trait filtered data, rename columns to jive with the rest of the script
bt_traitfiltered <- bt_traitfiltered
  rename_with(toupper) %>%
  rename(Species = SPECIES, StudyMethod = STUDYMETHOD, ObsEventID = OBSEVENTID,
         rarefyID = RAREFYID, cell = CELL, Abundance = ABUNDANCE, Biomass = BIOMASS)

load(here::here("data/trait_ref.rda"))
```

### 2022-04-27 analysis/04_collate_rarefied_null.Rmd
scrap the pins approach

## get null models
null_table <- pins::pin_get("null-table", board = "github")
```

@@

##	save
usethis::use_data(rarefied_metrics)

pins::board_register_github(name = "github", repo = "karinorman/biodivTS_data", branch = "master")
pins::pin(rarefied_metrics, board = "github")
```

>>>>

## get null models
load(here::here("data/null_table.rda"))
```

@@

##	save
usethis::use_data(rarefied_metrics)
```
